Shape Enhanced With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-15 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

% Paper title.
\title{Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh by enhancing the global object curvature. This method uses a
original extension of the Laplace Beltrami operator. Along with the
method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software blender.
\end{abstract}

@@

Interest in meshes composed of triangles and quads has lately increased
because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
Nowadays, many artists use a manual connection of a couple of vertices
to perform animation processes and interpolation \cite{Mullen2007}.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles. The curvature enhancement and shape
exaggeration can thus be used as such operator in the sculpting process,
when inflating a shape since current brushes end up by losing detail
when moving vertices \cite{Stanculescu2011}. In contrast, the presented
method inflates a mesh by moving the vertices towards the reverse
curvature direction, conserving the shape and sharp features of the
model.

@@

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for curvature enhancement and applications of subdivision
of surfaces and sculpting; finally some Laplacian operator results,
to hybrid quad/triangle meshes are graphically shown as well as results
of the curvature enhancement applications in sculpting, subdivision
and modeling.

@@

If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is
normalized by the total area of the first neighborhood around $v_{i}$,
the \textit{discrete mean curvature normal} of a surface $S$ is obtained,
as shown in equation (\ref{eq:discrete_mean_curvature_normal}).

@@

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$.

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
or triangle $\ensuremath{A\left(T_{N_{1}\left(v_{i}\right)}\right)}$
to vertex $\ensuremath{v_{i}}$ in $M$ is.

\begin{center}
$A\left(v_{i}\right)=A\left(Q_{N_{1}\left(v_{i}\right)}\right)+A\left(T_{N_{1}\left(v_{i}\right)}\right)$.
\par\end{center}

@@

Applying the mean average area, according to \cite{Xiong2011}, from
all possible triangulations, as show in figure \ref{fig:quad_xiong},
the area for each quad $\ensuremath{A\left(Q_{N_{1}\left(v_{i}\right)}\right)}$
is

@@

Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{N_{1}\left(v_{i}\right)}$.

@@

\begin{equation}
\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
\end{equation}

@@

\begin{equation}
w_{ij}=\begin{cases}
\left(\cot\alpha_{j}+\cot\beta_{j}\right) & \mbox{case }\mathit{a.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}+\cot\theta_{j3}+\cot\theta_{j6}\right) & \mbox{case \ensuremath{\mathit{b}}.}\\
\left(\cot\theta_{j2}+\cot\theta_{j5}\right) & \mbox{case \ensuremath{\mathit{c}}.}\\
\frac{1}{2}\left(\cot\theta_{j3}+\cot\theta_{j6}\right)+\cot\beta_{j} & \mbox{case \ensuremath{\mathit{d}}.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
\end{cases}\label{eq:TQLBO_wij}
\end{equation}

@@

\subsection{The Curvature Enhancement\label{sub:Curvature-Enhancing}}

@@

\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
from a coarse model: the curvature, obtained from the Catmull-Clark
Subdivision, is enhanced. Soft constraints, over the coarse model,
is drawn in red.}

@@

The curvature is enhanced by using the reverse direction of the curvature
flow, moving the vertices towards those mesh portions with larger
curvature. A standard diffusion process is applied:

@@

The vertices $V^{t+1}$ are enhanced, along their reverse curvature
direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, and $\lambda dt$

is the enhancement factor that supports negative and positive values:
negative for enhancement and positive for smoothing.

The method was devised to use with weighted vertex groups, which specify
the final curvature enhancement of the solution, meaning $0$ as no
changes and 1 when a maximal change is applied. The weights modify
the influence zones, where the Laplacian is applied, as shown in equation
\ref{eq:Lineal_System_with_wp}. Interestingly, the generated family
of shapes may change substantially with the weights of specific control
points.

@@

\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
Subdivision. Models with Laplacian smoothing: (c) $\lambda=60.0$,
$\lambda_{e}=12.0$ and (d) $\lambda=90.0$, $\lambda_{e}=80.0$.
Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying curvature enhancement: (e) $\lambda=-200.0$,
$\lambda_{e}=12.0$ and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
\end{figure*}

A new sculpting brush is herein proposed and aims to inflate the shape,
magnifying the shape curvatures of a polygon mesh in real time. This
brush works properly with the stroke method \textsl{Drag Dot}, allowing
to pre-visualize the model changes before the mouse is released. Also,
it allows to move the mouse along the model to match the curvature
zone which is supposed to be enhanced.

@@

Catmull-Clark subdivision surface methods generate smooth and continuous
models from a coarse model and produce quick results because of the
simplicity of implementation. Nevertheless, changes to the global
curvature are hardly implantable. The Catmull-Clark subdivision surfaces
together with curvature enhancement can easily generate families of
shapes by changing a single parameter, allowing to handle a model
with very few vertices. In practice, this would allow an artist to
choose a model from a similar set of options that would meet his/her
needs without having to change each of the control vertices. Likewise,
the presented method allows the use of vertex weight paint over the
control points. The weights can be applied to a coarse model, followed
by a Catmull-Clark subdivision where weights are interpolated, producing
weights with smooth changes in the influence zones, as shown in figure
\ref{fig:Subdivision-Cups}.c.

@@

The results of the curvature enhancement method with the extension
of the Laplace Beltrami operator for hybrid quad/triangle meshes with
several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
\ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
\ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
\ref{fig:Animated_Camell}). The curvature enhancement was assessed
with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz
and 8 GB RAM.

@@

Laplacian smoothing applied with simple subdivision may produce similar
results to those obtained with Catmull-Clark, whose models are in
average equal triangles, as shown in figure \ref{fig:Catmull_Clark},
(b) Catmull-Clark, (c) Laplacian smoothing. The one obtained with
the Laplacian smoothing is shown in panel (c), (d) and those curvature
modified versions are in (e) and (f). As can be observed, different
versions of the original sketch can be obtained by parameterizing
a single model value, a great advantage of the presented method. Figure
\ref{fig:camello_enhanced} shows the generation of different versions
of a camel according to the $\lambda$ parameter. In the top row,
it is shown the curvature enhancement results, as $\lambda$ becomes
larger and negative, the resultant shape is observed as if the model
would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
The larger the $\lambda$ parameter the larger the model feature enhancements.
The bottom row of figure \ref{fig:camello_enhanced} shows the use
of weighted vertex groups, specifying which areas will be enhanced.
On the left, the enhancement of the camel legs produces an organic
aspect, notice that the border is not distorted and smooth.

@@

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
the head and neck.}
\end{figure}

@@

Figure \ref{fig:Sculpt_Brush} shows the use of a curvature enhancement
brush for sculpting in real time. One pass was used with the brush,
as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
the camel foot shows the inflation intersection that looks like two
bubbles, a similar pattern to what is observed to the fingers on the
bottom of the same figure. The silhouette enhancement is observed
in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
together with its finger and leg details. Similar results can be obtained
by a user, however it would take several steps and require the use
of several brushes, while the curvature enhancement took a single
step. Likewise, this new method can easily enhance organic features
like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
the curvature enhancement brush performance is illustrated, in this
experiment three models with 12K, 40K and 164K vertices, were used.
These models were sculpted with the curvature enhance brush, at each
step the brush sphere containing a variable number of vertices for
processing. The processing time for 800 vertices in the camel paw
(40k model) only took 0.1 seconds, for 2600 vertices in the leg and
neck (model 40k) took 0.5 seconds, these times are suitable in real
applications since an artist sculpts a model for parts, and each part
is represented by an average of about 3000 vertices.

Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
produce similar results if the triangles that compose the mesh are
about the same size. The normalized version is more stable and predictable
because it is not divided by the area of the ring which may be very
small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c
bottom row. The curvature enhancement of the model with the normalized
Laplacian operator results in a more regular pattern. The model can
be deformed with a TQLBO normalized version with large $\lambda$
($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}
shows different results due to the triangle areas in the model. Triangles
with larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
skull), and smaller triangles have larger enhancements (figure \ref{fig:(a)Monkey}.c
chin).

@@

\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
for leg into blue circle, (c) Enhance curvature brush for leg into
red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
blue circle, (c) Curvature enhancement brush for fingers in red circle.}
\end{figure}

@@

\caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
enhancement brush in terms of the sculpted vertices per second. Three
models with 12K, 40K, 164K vertices used for sculpting in real time.}
\end{figure}

@@

\caption{\label{fig:Animated_Camell}The method is pose insensitive. The enhancement
for the different poses are similar in terms of shape. Top row: Original
walk cycle camel model. Bottom row: Curvature enhancement with weight
vertex group, $\lambda=-400$ and $2$ iterations. }
\end{figure*}

@@

The curvature cannot be calculted at the border of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by

Desbrun et al. \cite{Desbrun1999}.

@@

We show that this tool may work in early modeling stages, case in
which coarse models are used, allowing to modify the curvature generated
by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
of the vertices with change of a single parameters.

>>>>

% Paper title.
\title{Shape Enhanced With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
$-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh that allows to set a family of possible shapes by controlling
a single parameter, the global curvature. The method uses an original
extension of the Laplace Beltrami operator that efficiently estimates
a curvature parameter which is used to define an enhanced shape after
a particular operation performed in certain mesh points. Along with
the method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software Blender.
\end{abstract}

@@

Interest in meshes composed of triangles and quads has lately increased
because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
Nowadays, many artists use a manual connection of a couple of vertices
to perform animation processes and interpolation \cite{Mullen2007}.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles. The shape enhancement and shape exaggeration
can thus be used as such brush in the sculpting process, when inflating
a shape since current brushes end up by losing detail when moving
vertices \cite{Stanculescu2011}. In contrast, the presented method
inflates a mesh by moving the vertices towards the reverse curvature
direction, conserving the shape and sharp features of the model.

@@

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for shape enhancement and applications of subdivision of
surfaces and sculpting; finally some Laplacian operator results, to
hybrid quad/triangle meshes are graphically shown as well as results
of the shape enhancement applications in sculpting, subdivision and
modeling.

@@

If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is
normalized by the total area of the $1$-ring neighborhood around
$v_{i}$, the \textit{discrete mean curvature normal} of a surface
$S$ is obtained, as shown in equation (\ref{eq:discrete_mean_curvature_normal}).

@@

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
corresponds to a sum of the quad faces $A\left(Q_{v_{i}}\right)$
and the areas of the triangular faces $\ensuremath{A\left(T_{v_{i}}\right)}$
adjacent to vertex $\ensuremath{v_{i}}$.

\begin{center}
$A\left(v_{i}\right)=A\left(Q_{v_{i}}\right)+A\left(T_{v_{i}}\right)$.
\par\end{center}

@@

Applying the mean average area, according to \cite{Xiong2011}, from
all possible triangulations, as show in figure \ref{fig:quad_xiong},
the area for each quad $\ensuremath{A\left(Q_{v_{i}}\right)}$ is

@@

Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{v_{i}}$ and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{v_{i}}$.

@@

{\small 
\begin{equation}
\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
\end{equation}
}{\small \par}

@@

{\small 
\begin{equation}
w_{ij}=\begin{cases}
\left(\cot\alpha_{j}+\cot\beta_{j}\right) & \mbox{case }\mathit{a.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}+\cot\theta_{j3}+\cot\theta_{j6}\right) & \mbox{case \ensuremath{\mathit{b}}.}\\
\left(\cot\theta_{j2}+\cot\theta_{j5}\right) & \mbox{case \ensuremath{\mathit{c}}.}\\
\frac{1}{2}\left(\cot\theta_{j3}+\cot\theta_{j6}\right)+\cot\beta_{j} & \mbox{case \ensuremath{\mathit{d}}.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
\end{cases}\label{eq:TQLBO_wij}
\end{equation}
}{\small \par}

@@

\subsection{The Shape Enhancement\label{sub:Curvature-Enhancing}}

@@

\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
Subdivision (b), (d), is enhanced. Soft constraints, over the coarse
model, is drawn in red and blue (c).}

@@

The shape is enhanced by using the reverse direction of the curvature
flow, moving the vertices towards those mesh portions with larger
curvature. A standard diffusion process is applied:

@@

The vertices $V^{t+1}$ are enhanced, along their reverse curvature
direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, and $\lambda dt$ is the enhancement factor that supports negative
and positive values: negative for enhancement and positive for smoothing.

The method was devised to use with weighted vertex groups, which specify
the final shape enhancement of the solution, meaning $0$ as no changes
and 1 when a maximal change is applied. The weights modify the influence
zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
Interestingly, the generated family of shapes may change substantially
with the weights of specific control points.

The curvature cannot be calculted at the boundary of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by Desbrun et al. \cite{Desbrun1999}, the enhancement factor
for boundary is represented by $\lambda_{e}$.

@@

\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
Subdivision. Models with Laplacian smoothing: (c) $\lambda=60.0$,
$\lambda_{e}=12.0$ and (d) $\lambda=90.0$, $\lambda_{e}=80.0$.
Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying shape enhancement: (e) $\lambda=-200.0$, $\lambda_{e}=12.0$
and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
\end{figure*}

A new sculpting brush is herein proposed and aims to inflate the shape,
magnifying the shape curvatures of a polygon mesh in real time. This
brush works properly with the stroke method \textsl{Drag Dot}, allowing
to pre-visualize the model changes before the mouse is released. Also,
it allows to move the mouse along the model to match the shape zone
which is supposed to be enhanced.

@@

Catmull-Clark subdivision surface methods generate smooth and continuous
models from a coarse model and produce quick results because of the
simplicity of implementation. Nevertheless, changes to the global
curvature are hardly implantable. The Catmull-Clark subdivision surfaces
together with shape enhancement can easily generate families of shapes
by changing a single parameter, allowing to handle a model with very
few vertices. In practice, this would allow an artist to choose a
model from a similar set of options that would meet his/her needs
without having to change each of the control vertices. Likewise, the
presented method allows the use of vertex weight paint over the control
points. The weights can be applied to a coarse model, followed by
a Catmull-Clark subdivision where weights are interpolated, producing
weights with smooth changes in the influence zones, as shown in figure
\ref{fig:Subdivision-Cups}.c.

@@

The results of the shape enhancement method with the extension of
the Laplace Beltrami operator for hybrid quad/triangle meshes with
several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
\ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
\ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
\ref{fig:Animated_Camell}). The shape enhancement was assessed with
TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz and 8
GB RAM.

@@

Laplacian smoothing applied with simple subdivision may produce similar
results to those obtained with Catmull-Clark, whose models are in
average equal triangles. Figure \ref{fig:Catmull_Clark}.b. shows
Catmull-Clark subdivision , \ref{fig:Catmull_Clark}.c. shows Laplacian
smoothing. The one obtained with the Laplacian smoothing is shown
in panel (c), (d) and those curvature modified versions are in (e)
and (f). As can be observed, different versions of the original sketch
can be obtained by parameterizing a single model value, a great advantage
of the presented method. Figure \ref{fig:camello_enhanced} shows
the generation of different versions of a camel according to the $\lambda$
parameter. In the top row, it is shown the shape enhancement results,
as $\lambda$ becomes larger and negative, the resultant shape is
observed as if the model would inflate the more convex parts, as shown
in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
the larger the model feature enhancements. The bottom row of figure
\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
specifying which areas will be enhanced. On the left, the enhancement
of the camel legs produces an organic aspect, notice that the border
is not distorted and smooth.

@@

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Shape enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Shape enhancement with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
the head and neck.}
\end{figure}

@@

Figure \ref{fig:Sculpt_Brush} shows the use of a shape enhancement
brush for sculpting in real time. One pass was used with the brush,
as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
the camel foot shows the inflation intersection that looks like two
bubbles, a similar pattern to what is observed to the fingers on the
bottom of the same figure. The silhouette enhancement is observed
in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
together with its finger and foot details. Similar results can be
obtained by a user, however it would take several steps and require
the use of several brushes, while the shape enhancement took a single
step. Likewise, this new method can easily enhance organic features
like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
the shape enhancement brush performance is illustrated, in this experiment
three models with 12K, 40K and 164K vertices, were used. These models
were sculpted with the shape enhance brush, at each step the brush
sphere containing a variable number of vertices for processing. The
processing time for 800 vertices in the camel paw (40k model) only
took 0.1 seconds, for 2600 vertices in the leg and neck (model 40k)
took 0.5 seconds, these times are suitable in real applications since
an artist sculpts a model for parts, and each part is represented
by an average of about 1800 vertices.

Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
produce similar results if the triangles that compose the mesh are
about the same size. The normalized version is more stable and predictable
because it is not divided by the area of the ring which may be very
small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c
bottom row. The shape enhancement of the model with the normalized
Laplacian operator results in a more regular pattern. The model can
be deformed with a TQLBO normalized version with large $\lambda$
($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}.c
shows different results due to the triangle areas in the model. Triangles
with larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
skull), and smaller triangles have larger enhancements (figure \ref{fig:(a)Monkey}.c
chin).

@@

\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
for leg into blue circle, (c) Enhance shape brush for leg into red
circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
circle, (c) Shape enhancement brush for fingers in red circle.}
\end{figure}

@@

\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape enhancement
brush in terms of the sculpted vertices per second. Three models with
12K, 40K, 164K vertices used for sculpting in real time.}
\end{figure}

@@

\caption{\label{fig:Animated_Camell}The method is pose insensitive. The enhancement
for the different poses are similar in terms of shape. Top row: Original
walk cycle camel model. Bottom row: Shape enhancement with weight
vertex group, $\lambda=-400$ and $2$ iterations. }
\end{figure*}

@@

@@

We show that this tool may work in early modeling stages, case in
which coarse models are used, allowing to modify the shape generated
by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
of the vertices with change of a single parameters.
